The Probability of Convergent Evolution During Local Adaptation.

### 2014-07-03 patchy-selection-paper.tex
small changes throughout

\maketitle
\begin{center}
$^1$ Computational Biology and Bioinformatics \\ University of
Southern California, Los Angeles, CA
$^2$Center for Population Biology \& Department of Evolution and Ecology \\ University of California -- Davis. Davis, CA, 95616
\end{center}

@@

%%%%%%%%%%%
\section{Patchy selection} 
\label{ss:discretedemes}

>>>>

\maketitle
\begin{center}
$^1$ Computational Biology and Bioinformatics \\ University of
Southern California, Los Angeles, CA\\
$^2$Center for Population Biology \& Department of Evolution and Ecology \\ University of California -- Davis. Davis, CA, 95616
\end{center}

@@

%%%%%%%%%%%

\section{Patchy selection} 
\label{ss:discretedemes}
